Lichat, A Lightweight Chat Protocol

### 2022-01-25 els2022-lichat/paper.tex
Cite for matrix.

@@

\section{Further Work}\label{further-work}
On the protocol side, we would like to develop further extensions, primarily to allow for VOIP, federation, and encrypted messaging. Encryption and privacy are of especially big interest, though also pose quite challenging as end-to-end encrypted one-to-many communication is difficult to achieve efficiently\cite{nabeel2017many}\cite{whisper2014}.

>>>>

The Matrix core specification\cite{matrix} is extremely extensive. It covers a lot of ground including encryption, federation, and other advanced features supported by the protocol. Especially notable is that the protocol is quite complex and features a lot of out-of-stream APIs, whereas Lichat handles everything within the single stream between the user and the server.

@@

\section{Further Work}\label{further-work}
On the protocol side, we would like to develop further extensions, primarily to allow for VOIP, federation, and encrypted messaging. Encryption and privacy are of especially big interest, though are quite challenging, as end-to-end encrypted one-to-many communication is difficult to achieve efficiently\cite{nabeel2017many}\cite{whisper2014}.
